\documentclass{article}
\title{Sorting Algorithms.}
\author{Kamugisha Keith 12/u/6112/ps}
\begin{document}
METHODOLOGY FOR IMPLEMENTATION OF SORTING ALGORITHMS USING JAVASCRIPT. 
	
\subsection{Methodology}

\subsubsection{Introduction}
	This section presents the study area, methods and techniques that will be used in data collection, analysis and processing. It also includes the design of the research. 	

\subsubsection{Data collection techniques}
	To help us obtain objective 1, we shall use the following methods;
	
\subsubsection{Document Review}
	This will involve carrying out research and extensive reading of existing materials and documentation regarding sorting algorithms. Resources such as thesis will be utilized.
	
	To help us obtain objective 2, we shall use the following method;
	
\subsubsection{Implementation}
	The technologies that will be used during the implementation of this project will include programming languages like HTML and Javascript.

\subsubsection{Testing and Validation}
	
	To help us obtain objective 2, we shall use the following methods;
\subsubsection{Testing}
	Though Unit testing done after each module has been created and integration testing done as each of the created modules is assembled to work together and finally a system test after all the modules have been assembled to come up with the entire system.   
	
\subsubsection{Validation}
	The complete system will be presented to end user representatives who will try out the system and verify that the developed system addresses all the requirements and will satisfy all the intended objectives.
	
\end{document}